Imtiyaaz

### 2022-11-16 src/All variables.Rmd
Update All variables.Rmd

# Combine all performances into a single output
summary <- rbind(summary_model1, summary_ridge, summary_lasso)
rownames(summary) <- c("MLR", "Ridge_model", "LASSO_model" )
colnames(summary)[5] <- "R^2"
knitr::kable(summary, digits = 3)
```

>>>>

# Combine all performances into a single output
summary <- rbind(summary_model1, summary_ridge, summary_lasso)
rownames(summary) <- c("MLR", "Ridge_model", "LASSO_model" )
colnames(summary)[5] <- "R^2"
knitr::kable(summary, digits = 3)

```{r}
knitr::kable(summary_MLR, digits = 3)
knitr::kable(summary_ridge[,-5], digits = 3)
```
